Dataset-level report

### 2019-11-14 analysis/reports/dat_report_template.Rmd
fix bbs?

if(this_dataset == "misc_abund_short") {
  cache_loc = "miscabund"
} else{
  cache_loc = this_dataset
}

@@

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)
loadd(all_di, cache = cache)

>>>>

if(this_dataset == "misc_abund_short") {
  cache_loc = "miscabund"
} else if (this_dataset == "fia_short") {
  cache_loc = "fia" 
} else {
  cache_loc = this_dataset
}

@@

dat <- readd(paste0("dat_s_dat_", this_dataset), cache = cache, character_only = T)

loadd(all_di, cache = cache)
